|

### 2020-07-28 paper.Rmd
Fig 1 updated.

XXX FIX - how can I make the contours better? Maybe get radial density and draw as circles?
For illustration we show two-dimensional linear projections of points sampled uniformly within hyperspheres in $p=3, 10, 100$ dimensions in Figure \ref{fig:density}. All distributions are uniform within the maximum radius $R=1$, but the projected points start piling near the center as $p$ increases.

```{r density, fig.cap="Two-dimensional projections of 10k points sampled uniformly within a $p$-dimensional hyperspheres, for $p=3, 10, 100$. The density is shown both through transparancy of the projected points, and as contour lines.", out.width="95%", fig.align = "center"}

@@

lbl <- c("p=3", "p=10", "p=100")
names(lbl) <- c("p3", "p10", "p100")

@@

proj_points <- as_tibble(rbind(p3, p10, p100)) %>%
  mutate(p = c(rep(3, n), rep(10, n), rep(100, n)))

ggplot(proj_points, aes(x, y)) +
  #geom_point(alpha=0.02) + 
  #geom_density2d(bins = 7, contour_var = "ndensity") +
  geom_hex(bins = 12, aes(fill=log(..count..))) +
  #geom_hex(bins = 12) +
  scale_fill_viridis_c() +
  coord_fixed() +
  theme_bw() +
  facet_wrap(~p, labeller = labeller(name = lbl)) +
  #guides(color = FALSE) +
  theme(axis.title.x=element_blank(), axis.title.y=element_blank())

### a radial binning
n <- 5
r_breaks <- seq(0, 1, length.out = n+1)
proj_points_rbin <- proj_points %>%
  mutate(r = sqrt(x^2 + y^2)) %>%
  mutate(bin = cut(r, r_breaks)) %>%
  mutate(bin_up = as.numeric( sub("[^,]*,([^]]*)\\]", "\\1", bin))) %>%
  group_by(p) %>%
  count(bin_up) %>%
  arrange(-bin_up)

ggplot(proj_points_rbin) +
  geom_circle(aes(x0= 0, y0=0, r = bin_up, fill=log(n))) +
  scale_fill_viridis_c() +
  facet_wrap(~p, labeller = labeller(name = lbl)) +
  coord_fixed() +
  theme_bw()

>>>>

For illustration we show histograms of two-dimensional linear projections of points sampled uniformly within hyperspheres in $p=3, 10, 100$ dimensions in Figure \ref{fig:density}. All distributions are uniform within the maximum radius $R=1$, but the projected points start piling near the center as $p$ increases.

```{r density, fig.cap="Histogram of two-dimensional projections of 10k points sampled uniformly within a $p$-dimensional hyperspheres, for $p=3, 10, 100$. The fill color shows the logarithm of the bin count, with the highest counts shown in yellow. As $p$ increases the samples concentrate near the center.", out.width="95%", fig.align = "center"}

@@

@@

proj_points <- as_tibble(rbind(p3, p10, p100)) %>%
  mutate(p = factor(c(rep("p = 3", n), rep("p = 10", n), rep("p = 100", n)), levels = c("p = 3", "p = 10", "p = 100")))

ggplot(proj_points, aes(x, y)) +
  geom_hex(bins = 20, aes(fill=log(..count..))) +
  scale_fill_viridis_c() +
  theme_bw() +
  facet_wrap(~p, scales = "free") +
  guides(fill = FALSE) +
  theme(axis.title.x=element_blank(), axis.title.y=element_blank(), aspect.ratio = 1)
